Large and Infinitary Quotient Inductive-Inductive Types

### 2020-01-10 draft/paper.tex
= instead of := when just unfolding definitions
s
not necessarily third, fourth, hence use Ty, Tm

\begin{definition}[The $\Set$ model of $\ToS$] For each $i$ and $j$, we have $\bA : \ToS_{\max(i+1, j)+1, j}$, which can be given by restricting the $\bM_{i,j}$ model
of Section \ref{sec:semantics} so that we only have the first $\Con$ components
in the interpretations for contexts, substitution, types, term, and we only have
actions on contexts in the interpretations of term and substitution
formers. Hence, we have:
\begin{alignat*}{3}
  & \Con_{\bA} && := \Set_{\max(i+1, j)} \\
  & \Sub_{\bA}\,\Gamma\,\Delta && := \Gamma \ra \Delta\\
  & \Ty_{\bA}\,\Gamma && := \Gamma \ra \Set_{\max(i+1, j)}\\
  & \Tm_{\bA}\,\Gamma\,A && := (\gamma : \Gamma) \ra A\,\gamma
\end{alignat*}
Now, for some $\Gamma : \Con_{\syn_j}$, the type of $\Gamma$-algebras at level
$i$ is given by $\llb\Gamma\rrb_{\bA}$, where we implicitly lift $\syn_j :
\ToS_{j+1, j}$ to $\ToS_{\max(i+1,j)+1, j}$. E.g.\, $\llb\NatSig\rrb_{\bA}$
yields a left-nested $\Sigma$-type of pointed sets with an endofunction. Also,
$\llb\Gamma\rrb_{\bM}$ extends $\llb\Gamma\rrb_{\bA}$ to an flCwF of
$\Gamma$-algebras, and $\llb\Gamma\rrb_{\bA} = \Con_{\llb\Gamma\rrb_{\bM}}$.
\end{definition}

\begin{definition}[Logical predicate model of $\ToS$ over the $\Set$ model]
For each $i$ and $j$ level we have $\bD$, which is a displayed $\ToS$ model over
$\bA$. This model, analogously to $\bA$, is given by restricting $\bM_{i,j}$ to
the \emph{third} components everywhere, corresponding to types or actions on
types. Hence, we have:
\begin{alignat*}{3}
  & \Con_{\bD}\,\ulGamma && := \ulGamma \ra \Set_{\max(i+1, j)} \\
  & \Sub_{\bD}\,\Gamma\,\Delta\,\ulsigma && := (\ulgamma : \ulGamma) \ra \Gamma\,\gamma \ra \Delta(\llb\ulsigma\rrb_{\bA}\,\ulgamma)\\
  & \Ty_{\bD}\,\Gamma\,\ulA && := (\ulgamma : \ulGamma) \ra \Gamma\,\ulgamma \ra \llb\ulA\rrb_{\bA}\,\ulgamma \ra \Set_{\max(i+1, j)}\\
  & \Tm_{\bD}\,\Gamma\,A\,\ult && := (\ulgamma : \ulGamma)(\gamma : \Gamma\,\ulGamma)
    \ra A\,\ulgamma\,\gamma\,(\llb\ult\rrb_{\bA}\,\ulgamma)
\end{alignat*}
\end{definition}

@@

\begin{definition}[Displayed algebra section model of $\ToS$] Analogously to
$\bA$ and $\bD$, for each $i$ and $j$ levels we define $\bS$ as a displayed
$\ToS$ model over the total model of $\bD$, which is given by restricting
$\bM_{i,j}$ to the fourth components, corresponding to interpretations of terms and
actions on terms.

>>>>

\begin{definition}[The $\Set$ model of $\ToS$] For each $i$ and $j$, we have $\bA : \ToS_{\max(i+1, j)+1, j}$, which can be given by restricting the $\bM_{i,j}$ model
of Section \ref{sec:semantics} so that we only have the first $\Con$ components
in the interpretations for contexts, substitution, types, term, and we only have
actions on contexts in the interpretations of term and substitution
formers. Hence, we have:
\begin{alignat*}{3}
  & \Con_{\bA} && = \Set_{\max(i+1, j)} \\
  & \Sub_{\bA}\,\Gamma\,\Delta && = \Gamma \ra \Delta\\
  & \Ty_{\bA}\,\Gamma && = \Gamma \ra \Set_{\max(i+1, j)}\\
  & \Tm_{\bA}\,\Gamma\,A && = (\gamma : \Gamma) \ra A\,\gamma
\end{alignat*}
Now, for some $\Gamma : \Con_{\syn_j}$, the type of $\Gamma$-algebras at level
$i$ is given by $\llb\Gamma\rrb_{\bA}$, where we implicitly lift $\syn_j :
\ToS_{j+1, j}$ to $\ToS_{\max(i+1,j)+1, j}$. E.g.\, $\llb\NatSig\rrb_{\bA}$
yields a left-nested $\Sigma$-type of pointed sets with an endofunction. Also,
$\llb\Gamma\rrb_{\bM}$ extends $\llb\Gamma\rrb_{\bA}$ to an flCwF of
$\Gamma$-algebras, and $\llb\Gamma\rrb_{\bA} = \Con_{\llb\Gamma\rrb_{\bM}}$.
\end{definition}

\begin{definition}[Logical predicate model of $\ToS$ over the $\Set$ model]
For each $i$ and $j$ level we have $\bD$, which is a displayed $\ToS$ model over
$\bA$. This model, analogously to $\bA$, is given by restricting $\bM_{i,j}$ to
the $\Ty$ components everywhere, corresponding to types or actions on
types. Hence, we have:
\begin{alignat*}{3}
  & \Con_{\bD}\,\ulGamma && = \ulGamma \ra \Set_{\max(i+1, j)} \\
  & \Sub_{\bD}\,\Gamma\,\Delta\,\ulsigma && = (\ulgamma : \ulGamma) \ra \Gamma\,\gamma \ra \Delta\,(\ulsigma\,\ulgamma)\\
  & \Ty_{\bD}\,\Gamma\,\ulA && = (\ulgamma : \ulGamma) \ra \Gamma\,\ulgamma \ra \ulA\,\ulgamma \ra \Set_{\max(i+1, j)}\\
  & \Tm_{\bD}\,\Gamma\,A\,\ult && = (\ulgamma : \ulGamma)(\gamma : \Gamma\,\ulGamma)
    \ra A\,\ulgamma\,\gamma\,(\ult\,\ulgamma)
\end{alignat*}
\end{definition}

@@

\begin{definition}[Displayed algebra section model of $\ToS$] Analogously to
$\bA$ and $\bD$, for each $i$ and $j$ levels we define $\bS$ as a displayed
$\ToS$ model over the total model of $\bD$, which is given by restricting
$\bM_{i,j}$ to the $\Tm$ components, corresponding to interpretations of terms and
actions on terms.
